---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# runner

<!-- badges: start -->
<!-- badges: end -->

Compute counts and statistics of occurrence of events in sequences that meets a criterion.

## Installation

You can install the development version of runner from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rfsaldanha/runner")
```

## Example

On this vector, how many sequences have at least 3 consecutive observations with value equal or greater than 5?

```{r example}
library(runner)

vec <- c(8,15,20,8,1,7,8,0,-2,5,9,12,0,-1,4,2,3,1)

trle_cond(vec, a_op = "gte", a = 3, b_op = "gte", b = 5)
```

And how many sequences have exactly 3 consecutive observations with value equal or greater than 5?

```{r}
trle_cond(vec, a_op = "e", a = 3, b_op = "gte", b = 5)
```

