---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `runner` package helps to count and compute statistics of events that occur in sequences that meet some conditions.

As an example, let's use the `airquality` dataset. It contains daily air quality measurements in New York, from May to September 1973.

```{r}
library(runner)
data("airquality")

head(airquality)
```

## Examples

First, let's consider the temperature measurements taken in June.

```{r}
june_data <- subset(airquality, Month == 6)
```

```{r}
library(ggplot2)

ggplot(june_data, aes(x = Day, y = Temp)) +
  geom_line() +
  geom_point() +
  theme_bw()
```

> How many times we had **three days or more** in a row, with temperatures **above** 83F?

To answer this question, first look at the plot.

```{r}
ggplot(june_data, aes(x = Day, y = Temp)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 83, color = "red") +
  theme_bw()
```

There are two sequences of days with temperatures above 83F. One with two days, and one with 5 days. This last sequence meets the condition of "three days or more".

Now, let's use the `runner` package to compute this for us.

```{r}
trle_cond(june_data$Temp, a_op = "gte", a = 3, b_op = "gte", b = 83)
```

> How many times we had **two days or more** with temperatures **below** 75F?

```{r}
ggplot(june_data, aes(x = Day, y = Temp)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 75, color = "red") +
  theme_bw()
```

```{r}
trle_cond(june_data$Temp, a_op = "gte", a = 2, b_op = "lte", b = 75)
```

## Grouping

You can use the `runner` functions inside `?dplyr::summarise` to compute counts for groups.

> For each month, how many sequences of three days or more presented temperatures above the month's average.

```{r, message=FALSE}
library(dplyr)

airquality |>
  summarise(
    avg = mean(Temp, na.rm = TRUE),
    count_3 = trle_cond(Temp, a_op = "gte", a = 3, b_op = "gte", b = avg), 
    .by = Month
  )
  
```

```{r}
month_avg <- airquality |>
  summarise(
    avg = mean(Temp, na.rm = TRUE),
    .by = Month
  )

airquality |>
  left_join(month_avg, by = "Month") |>
  mutate(date = as.Date(paste0(1973,"-",Month,"-",Day))) |> 
  ggplot(aes(x = date)) +
    geom_line(aes(y = Temp)) +
    geom_step(aes(y = avg), color = "red") +
    geom_point(aes(y = Temp)) +
    theme_bw()
```
